R5R

### 2020-08-21 r-package/tests_marcus/tests r5r.Rmd
Updated documentation and test.rmd

paths_df <- detailed_itineraries(r5r_core = r5r_core, origins = origin, destinations = destination, 
                     departure_datetime = trip_date_time, max_walk_dist = 800, mode = c("WALK", "BUS"),
                     shortest_path = FALSE, verbose = FALSE)

@@

```{r}
paths_df %>%
  ggplot() +
  geom_sf(data=street_net$edges, colour="grey85", aes(geometry=geometry)) +
  geom_sf(aes(geometry=geometry, colour=mode)) +
  facet_wrap(~option)
```
```{r}

@@

```{r}
ttm <- travel_time_matrix(r5r_core, points, points, departure_datetime = trip_date_time, 
                          mode=c("WALK", "BUS"), 
                          max_walk_dist = 500, max_trip_duration = 120L)
```

>>>>

paths_df <- detailed_itineraries(r5r_core = r5r_core, origins = origin, destinations = destination, 
                     departure_datetime = trip_date_time, max_walk_dist = 0.8, 
                     mode = c("WALK", "BICYCLE", "BUS"),
                     shortest_path = FALSE, verbose = FALSE)

@@

```{r}
paths_df %>%
  ggplot() +
  # geom_sf(data=street_net$edges, colour="grey85", aes(geometry=geometry)) +
  geom_sf(aes(geometry=geometry, colour=mode)) +
  facet_wrap(~option)
```
```{r}

@@

```{r}
ttm <- travel_time_matrix(r5r_core, points, points, departure_datetime = trip_date_time, 
                          mode=c("WALK", "BUS"), 
                          max_walk_dist = 500, max_trip_duration = 120L, verbose = FALSE)
```
